Efficient Handling of String-Number Conversion

### 2020-03-31 final-version/evaluation.tex
Update evaluation.tex

We compare {\tool} \changed{(\texttt{1e715b7dab})} with other state-of-the-art string solvers, namely, CVC4~(45bcf28ab)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3Str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}. For these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version. \changed{Observe that CVC4 and Z3 are  DPLL(T)-based string solvers.}
We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support all string functions in our benchmarks, especially string-number conversion.

We perform two sets of experiments. In the first set of experiments, we compare {\tool} with other tools on existing benchmarks over basic string constraints. Those benchmarks do not involve string-number conversion function. In the second set of experiments, we compare {\tool} with the other tools on new suites focusing on string-number conversion. Our goals of experiments are the following:
\smallskip

>>>>

We compare {\tool} \changed{(\texttt{1e715b7dab})} with other state-of-the-art string solvers, namely, CVC4~(45bcf28ab)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3Str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}. For these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version. \changed{Observe that CVC4 and Z3 are  DPLL(T)-based string solvers.}
We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occur in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support many of the string functions in our benchmarks, especially string-number conversion.

We perform two sets of experiments. In the first set of experiments, we compare {\tool} with other tools on existing benchmarks over basic string constraints. Those benchmarks do not involve string-number conversion functions. In the second set of experiments, we compare {\tool} with the other tools on new suites focusing on string-number conversion. Our goals of experiments are the following:
\smallskip
